Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-21 paper/main.tex
restructure & rephrase suppl. materials

\todo{print contrasts; count per category? -> pattern "average of events" and
counts vs. significant clusters?}

@@

\todo[inline]{SE: use different colormap for overlap of contrasts' clusters}
lche Kontraste (z.B. im Ergebnis) von anderen abgewichen?}

@@

% AD: results
In results from the analysis of the audio-description, all contrasts except
contrast 7 (\texttt{se\_new}, \texttt{se\_old} > non-spatial categories) and
contrast 8 (\texttt{se\_new} > non-spatial categories) yielded significant
bilateral clusters in anterior regions of the group PPA overlap
(Fig.~\ref{fig:stability-slices}).
% AD: RSC & LOC
Results from the analysis of the audio-description also yielded bilaterally
significant clusters in the ventral precuneus (all contrasts except contrasts 8)
and lateral occipital cortex (bilateral in contrasts 1 to 4; unilateral in
contrasts 6 and 7).
% concluding stament regarding PPA, RSC, and LOC
The results across the contrasts of the movie and audio-description indicate
that our findings regarding the PPA but also RSC and LOC are robust and do not
depend on the design of one specific contrasts.
%
\todo[inline]{print contrasts; counts per contrasted categories? "fit of
averaged events"?}
% but
Nevertheless, results are sensitive to the contrasted categories and the amount
of available data.
% example
For example, contrast 8 of the audio-description stimulus (\texttt{se\_new} >
\texttt{se\_old}) that used the most heterogeneous categories comprising the
least amount of events yielded neither a significant cluster in the
right-hemispheric nor left-hemispheric PPA.
% concluding statement
Hence, investigators that use model-driven analyses have to consider how many
events a naturalistic stimulus may provide and how homogeneous the events to be
averaged might be.

@@

\todo[inline]{following list probaly exhaustive but probably too long}
%
Lastly, some contrasts of the audio-description stimulus yielded significant
clusters in regions that were not statistically significant in three or more
contrasts.
% details
In detail, contrast 2 yielded clusters in the anterior cingulate gyrus
(bilateral), right frontal pole, right frontal medial cortex, and right putamen.
%
Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
frontal pole, and left insular.
%
Contrast 7 shows clusters in the left frontal pole and left frontal operculum,
left insular.
%
Contrast 6 shows one additional cluster in the right medial frontal cortex.
% concludion statement
Here again, significantly increased activation beyond areas known to be involved
in processing of spatial information can be attributed to stimulus features of
the naturalistic stimulus that were not sufficiently controlled leading to a
bias in the contrasts.

@@

% intro
We implemented five contrasts for every stimulus.
% AV: no_cut > x
In the analysis of the movie data, none of the four contrasts that compared the
\texttt{no\_cut} category to a movie cut category (Tab.~\ref{tab:av-contrasts})
yielded significant clusters.
% AV using nouns
The contrast that used the narrator's nouns that did not actually exist in the
movie stimulus (\texttt{se\_new} > \texttt{se\_old}) yielded a significant
cluster in the right PPA and bilateral clusters in the superior lateral
occipital cortices (the right hemispheric cluster extending into the superior
parietal cortex).\todo{explanation?}

% AD stimulus
For the analysis of the audio-description, we created control contrasts based on
events of the annotated movie cuts (Tab.~\ref{tab:ao-contrasts}), which although
invisible were nevertheless frequently perceivable due to changes in the
soundscape.
% contrast 9
Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the
left inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.\todo{explanation?}

The four control contrasts of the movie stimulus that compared the
\texttt{no\_cuts} to categories of movie cuts all lead to null results.
% AD anno in AV data
The movie contrast using nouns (\texttt{se\_new} > \texttt{se\_old}): PPA
(unilateral), LOC (bilateral); These noun categories show highest correlation
among nouns with their cut counterpart \texttt{se\_new} (nouns) is r$\approx$0.3
correlated with \texttt{vse\_new} (cuts); \texttt{se\_old} (nouns) is
r$\approx$0.4 correlated with \texttt{vse\_old}.

% AV anno in AV data
The the 5 movie PPA contrasts but with the movie data using cuts. All null
results except:
% contrast 9
vse\_new > pe\_old (conrast 9): left inferior prefrontal cortex (pars
triangularis) and right ventral precuneus/posterior cingulate gyrus.
% contrast 12
vse\_new > vse\_old, vpe\_old (contrast 12): one cluster in the right posterior
hippocampus.

>>>>

\todo[inline]{print contrasts; count per category? -> pattern "average of
events" and counts vs. significant clusters?}

@@

\todo[inline]{SE: use different colormap for overlap of contrasts' clusters}

@@

% AD: results
In results from the analysis of the audio-description, all contrasts except
contrast 7 (\texttt{se\_new}, \texttt{se\_old} > non-spatial categories) and
contrast 8 (\texttt{se\_new} > non-spatial categories) yielded significant
bilateral clusters in anterior regions of the group PPA overlap
(Fig.~\ref{fig:stability-slices}).
% AD: RSC & LOC
Results from the analysis of the audio-description also yielded bilaterally
significant clusters in the ventral precuneus (all contrasts except contrasts 8)
and lateral occipital cortex (bilateral in contrasts 1 to 4; unilateral in
contrasts 6 and 7).
% concluding stament regarding PPA, RSC, and LOC
The results across the contrasts of the movie and audio-description indicate
that our findings regarding the PPA but also RSC and LOC are robust and do not
depend on the design of one specific contrasts.
% but:
Nevertheless, results are sensitive to the contrasted categories and the amount
of available data.
% example
For example, contrast 8 of the audio-description stimulus (\texttt{se\_new} >
\texttt{se\_old}) that used the most heterogeneous categories comprising the
least amount of events yielded neither a significant cluster in the
right-hemispheric nor left-hemispheric PPA.
% concluding statement
Hence, investigators that use model-driven analyses have to consider how many
events a naturalistic stimulus may provide and how homogeneous the events to be
averaged might be.

@@

\todo[inline]{following list is exhaustive but probably too detailed}
%
Lastly, some contrasts of the audio-description stimulus yielded significant
clusters in regions that were not statistically significant in three or more
contrasts.
% details
In detail, contrast 2 yielded clusters in the anterior cingulate gyrus
(bilateral), right frontal pole, right frontal medial cortex, and right putamen.
%
Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
frontal pole, and left insular.
%
Contrast 7 shows clusters in the left frontal pole and left frontal operculum,
left insular.
%
Contrast 6 shows one additional cluster in the right medial frontal cortex.
% concludion statement
Here again, significantly increased activation beyond areas known to be involved
in processing of spatial information can be attributed to stimulus features of
the naturalistic stimulus that were not sufficiently controlled leading to a
bias in the contrasts.

@@

% intro
For each contrast we created several control contrasts.
% AV: no_cut > x
To test for XYZ\todo{yes, to test what?} within the movie fMRI data, we created
four contrasts that compared hemodynamic activity during frames within movie
shots (\texttt{no\_cut} category) with movie cut related categories (Tab.~\ref{tab:av-contrasts}).
%
None of these four contrasts yielded a significant cluster which suggest that
XYZ\todo{concluding statement}.

% \texttt{se\_new} (nouns) is r$\approx$0.3 correlated with \texttt{vse\_new}
% (cuts); \texttt{se\_old} (nouns) is r$\approx$0.4 correlated with
% \texttt{vse\_old}.
Given that cuts to a setting depicted for the first time (\texttt{vse\_new}) and
nouns indicating a a switch to a setting ocurring for the first timei
(\texttt{se\_new}), and cuts to a recurringly depicted setting
({\texttt{vse\_old}) and nouns indicating a switch a recurring setting
(\texttt{se\_old} turned out to be moderately correlated
(Fig.~\ref{fig:reg-corr}), we created a contrast that used the
audio-description's nouns on the movie data ({\texttt{se\_new} >
\texttt{se\_old}).
% results
The contrasts yielded a significant cluster in the right PPA and bilateral
clusters in the superior lateral occipital cortices (the right hemispheric
cluster extending into the superior parietal cortex).
%
Results suggest that XYZ.
\todo{concluding statement}

% AD stimulus
Finally for the analysis of the audio-description, we created control contrasts
based on events of the annotated movie cuts (Tab.~\ref{tab:ao-contrasts}) in
order to test XYZ.
\todo{why exactly did we do this except "we do not expect (lots of) significant cluster because negative control?}
%
Two of five contrasts yielded signficant clusters.
% contrast 9
Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the
left inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.
\todo{explanation?}
%
Overall results from the negative control contrast of the audio-description's
data suggest that XYZ.
\todo{concluding statement}.
